---
title: "Final Project Rmd"
author: "Nikhil Dhawan"
date: "`r Sys.Date()`"
output: html_document
---

# Let's load libraries
``` {r warnings=FALSE, results="hide"}
library(tidyverse)
library(tableone)
library(dplyr)
library(knitr)
library(Publish)
library(summarytools)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Let\'s input the data

ValueLabelFrequency%1Detox, 24-hour, hospital inpatient43,3902.6%2Detox, 24-hour, free-standing residential244,74714.7%3Rehab/residential, hospital (non-detox)4,2200.3%4Rehab/residential, short term (30 days or fewer)179,83010.8%5Rehab/residential, long term (more than 30 days)118,5457.1%6Ambulatory, intensive outpatient220,37813.2%7Ambulatory, non-intensive outpatient843,75450.6%8Ambulatory, detoxification11,5020.7%Total1,666,366100%Width: 2; Decimal: 0Variable Type: numeric


```{r}
load('/home/nikd/Dropbox/tedsd_puf_2018.RData')
```

# Let's look at the variables in the data set. 

```{r}
teds_puf_2017_cleaned <- tedsd_puf_2017 %>%  select(c(LOS, DAYWAIT, SERVICES,AGE))
teds_puf_2017_cleaned <- filter(tedsd_puf_2017, tedsd_puf_2017$SERVICES < 6)
teds_puf_2017_cleaned <- filter(teds_puf_2017_cleaned, tedsd_puf_2017$DAYWAIT > -1)
teds_puf_2017_cleaned <- filter(teds_puf_2017_cleaned, teds_puf_2017_cleaned$LOS > -1)
dfSummary(teds_puf_2017_cleaned) 
```

* Let's do some data analysis

Everything is significant!

```{r}
catTable <- CreateCatTable(vars=names(tedsd_puf_2017)[5:16], strata=c("DAYWAIT"),data = tedsd_puf_2017)
print(catTable) %>% kable()
```

# Let's find predictors of days waiting for treatment. 


```{r}
  teds_puf_2017_cleaned <- filter(tedsd_puf_2017, tedsd_puf_2017$DAYWAIT > -1)
  teds_puf_2017_cleaned <- filter(teds_puf_2017_cleaned, teds_puf_2017_cleaned$LOS > -1)
  lmfit <- lm(LOS ~ DAYWAIT, data = teds_puf_2017_cleaned)
  pubout <- publish(lmfit)

  with(teds_puf_2017_cleaned,cor.test(LOS,DAYWAIT))

  hist(lmfit$residuals,breaks = 50)

  hist(log(lmfit$residuals))

residsFitted <- data.frame(resid=lmfit$residuals,fitted=lmfit$fitted.values)
residsFitted$Prediction <- predict(lmfit,newdata = teds_puf_2017_cleaned)
residsFitted$DAYWAIT <- teds_puf_2017_cleaned$DAYWAIT

ggplot(residsFitted,aes(x=DAYWAIT,y=Prediction))+geom_point()
```
